Predicting the PCG PSeudo-Random Number Generator In Practice

### 2020-05-25 article/main.tex
maintenant ça compile

Let $\LCG_{n,k}(x, c)$ denote the vector
$(u_0, \dots, u_{n-1}) \in \mathbb{Z}_{2^k}$ (we will omit $n$ and $k$ when they
are obvious from the context).  It is easy to check that:
\begin{align}
  \label{eq:lcg-additive}
  \LCG_{n,k}(x + y, c + d) &= \LCG_{n,k}(x, c) + \LCG_{n,k}(y, d),  \\
  \label{eq:lcg-scalar}
  \LCG_{n,k}(\lamba x, \lambda c) = \lambda \LCG_{n,k}(x, c).

\end{align}

@@

Given a ``fresh'' output $X_i$, we can enumerate the 64 possible rotations
$r_i$; for each one, we can check whether
$(X_i \lll r_i)[0:\ell] = S_i[0:\ell] \oplus S_i[64:64+\ell]$. If none of the
rotations yields a match, then the guesses made beforehand have to be wrong. As
soon as $\ell \geq 6$, this test is efficient (and it can be done for any number
of fresh $X_i$'s). As a consequence, bad guesses can be filtered deterministically.

\begin{align*}
  \mathbf{S} &= \LCG(S_0, c) \\
             &= \LCG\left(S_0[0:\ell] + 2^\ell S_0[\ell:128], c[0:\ell] + 2^\ell c[\ell:128]\right) \\
             &= \LCG\left(S_0[0:\ell], c[0:\ell]) + 2^\ell \LCG\left(S_0[\ell:128],  c[\ell:128]\right) \\
  \Delta \mathbf{S} &= \LCG(S_1, c) - \LCG(S_0, c) \\
             &= \LCG(S_1 - S_0, 0)
\end{align*}

>>>>

Let $\LCG_{n,k}(x, c)$ denote the vector
$(u_0, \dots, u_{n-1}) \in \mathbb{Z}_{2^k}$ (we will omit $n$ and $k$ when they
are obvious from the context).  It is easy to check that:
\begin{align}
  \label{eq:lcg-additive}
  \LCG_{n,k}(x + y, c + d) &= \LCG_{n,k}(x, c) + \LCG_{n,k}(y, d),  \\
  \label{eq:lcg-scalar}
  \LCG_{n,k}(\lambda x, \lambda c) &= \lambda \LCG_{n,k}(x, c).   
\end{align}

@@

Given a ``fresh'' output $X_i$, and assuming that the guesses are correct, then we should have:
\[
  S_i[0:\ell] \oplus S_i[64:64+\ell] \in \bigl\{ (X_i \lll r_i)[0:\ell]~|~r_i=0, 1, \dots, 63 \bigr\}.
\]
If none of the rotations yields a match, then the guesses made beforehand have
to be wrong. As soon as $\ell \geq 6$, this test is efficient (and it can be
done for any number of fresh $X_i$'s). As a consequence, bad guesses can be
filtered deterministically.

\begin{align*}
  \mathbf{S} &= \LCG(S_0, c) \\
             &= \LCG\left(S_0[0:\ell] + 2^\ell S_0[\ell:128], c[0:\ell] + 2^\ell c[\ell:128]\right) \\
             &= \LCG\left(S_0[0:\ell], c[0:\ell]\right) + 2^\ell \LCG\left(S_0[\ell:128],  c[\ell:128]\right) \\
  \Delta \mathbf{S} &= \LCG(S_1, c) - \LCG(S_0, c) \\
             &= \LCG(S_1 - S_0, 0)
\end{align*}
